Uncertainty propagation in deep neural networks for sparse coding

### 2018-03-08 paper/BayesianLISTA.tex
added second synthetic experiment

In the Figure \ref{fig:number_of_layers_synthetic} prediction performance for increasing number of layers is presented. The proposed algorithm is superior in terms of NMSE

\begin{figure*}[t]
\subfloat[NMSE on train]{\includegraphics{graphics/synthetic_number_of_layers/nmse_train}}
~
\subfloat[NMSE on validation]{\includegraphics{graphics/synthetic_number_of_layers/nmse_validation}}
\newline
\subfloat[F measure on train]{\includegraphics{graphics/synthetic_number_of_layers/f_measure_train}}
~
\subfloat[F measure on validation]{\includegraphics{graphics/synthetic_number_of_layers/f_measure_validation}}
\caption{Number of layers on synthetic data}
\label{fig:number_of_layers_synthetic}
\end{figure*}

We compare two versions of the proposed Bayesian LISTA: with shared weight matrices and with individual matrices at each layer --- and LISTA.

>>>>

In the Figure \ref{fig:number_of_layers_synthetic} prediction performance for different number of layers $L$ is presented. The observation size is set as $K=50$.

In the Figure \ref{fig:unsersampling_synthetic} prediction performance for different observation sizes $K$ is presented. The number of layers is set as $L=4$.

\begin{figure}[t]
\subfloat[NMSE on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
~
\subfloat[NMSE on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}}
\newline
\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_train}}
~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}}
\caption{Number of layers on synthetic data}
\label{fig:number_of_layers_synthetic}
\end{figure}

\begin{figure}[t]
\subfloat[NMSE on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_train}}
~
\subfloat[NMSE on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_validation}}
\newline
\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_train}}
~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}}
\caption{Size of observations on synthetic data}
\label{fig:unsersampling_synthetic}
\end{figure}

%We compare two versions of the proposed Bayesian LISTA: with shared weight matrices and with individual matrices at each layer --- and LISTA.
